---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

The Network Risk Measures (`NetworkRiskMeasures`) package implements some risk measures for (financial) networks, such as DebtRank, Impact Susceptibility, Impact Diffusion and Impact Fluidity. 

## CRAN

The package will soon be on CRAN. We are still implementing some unit testing. 


## How to install the development version from GitHub

To install the GitHub version you need to have the package `devtools` installed. Make sure to set the option `build_vignettes = TRUE` to compile the package vignette (which is not available yet). 

```{r, eval = FALSE}
# install.packages("devtools") # run this to install the devtools package
devtools::install_github("carloscinelli/NetworkRiskMeasures", build_vignettes = TRUE)
```

## We are looking for interesting public datasets!

Most data that we use are confidential, so we can't use them as examples on the package. We are looking for interesting, public datasets on bilateral exposures to use as examples for the package. So if you have a suggestion, please do let us know!

## Example usage

To be expanded.

```{r}
library(NetworkRiskMeasures)

# Creating example data
## Assets Matrix (bilateral exposures)
assets_matrix <- matrix(c(0, 10, 3, 1, 0, 2, 0, 3, 0), ncol = 3)
rownames(assets_matrix) <- colnames(assets_matrix) <- letters[1:3]

## Capital Buffer
buffer <- c(a = 2, b = 5, c = 2)

## Measures based on the communicability matrix
## Impact Susceptibility, Fluidity and Diffusion
impact_susceptibility(assets_matrix, buffer)
impact_fluidity(assets_matrix, buffer)
impact_diffusion(assets_matrix, buffer)

## "Size" of the nodes
weights <-  c(a = 10, b = 100, c = 30)

# DebtRank - computes stress for each node considering its default
debt_rank(assets_matrix, buffer, weights)

# Arbitray shock -- 10% stress shock in each node
shock <- c(a = 0.1, b = 0.1, c = 0.1)
debt_rank_shock(assets_matrix, buffer, shock, weights)

```


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
